\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-15 paper.tex
finished variable declaration and modified input & output

    \subsubsection{Variable Declaration}
    \subsubsection{Input and Output}
    \subsubsection{Variable Assignment}
    \subsubsection{While Loop}

>>>>

    In this section, the approaches used to parse the statements of our programming language will be illustrated. Thanks to the \textit{result} parser and the \textit{bind} operator, this process has been simplified to a great extent and parsers are much more readable.

    \subsubsection{Variable Declaration}

    The simple programming language used for this case study contains only two types of variables: \textbf{Strings} and \textbf{Integers}. The declaration of a variable contains the following format: a keyword (either \textit{String} or \textit{Integer}), a space, a variable name (list of characters), a space, an equality operator, a space, a number for integer declaration or a string surrounded in single quotes for string declaration. \\ \\
    Keeping in mind the format, the construction of the \textbf{parse\textunderscore declaration\textunderscore string} and \\ \textbf{parse\textunderscore declaration\textunderscore int} is rather straightforward since all the parsers needed to construct these parsers have already been defined on section 5.

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    parse_declaration_string :: Parse AST
    parse_declaration_string = 
        tokenize "String " `bind` \string -> isword 
                           `bind` \id -> tokenize " = "          
                           `bind` \eq -> singleChar '\''  
                           `bind` \startQuote -> isword 
                           `bind` \word -> singleChar '\''    
                           `bind` \endQuoute -> 
        result (DeclarationString id (startQuote : word ++ [endQuoute])) 
     \end{lstlisting}
    \end{tcolorbox}

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
     parse_declaration_int :: Parse AST 
     parse_declaration_int = 
        tokenize "Integer " `bind` \integer -> isword 
                            `bind` \id -> tokenize " = " 
                            `bind` \eq -> is_number 
                            `bind` \num ->
        result (DeclarationInt id (read num :: Int) ) 
     \end{lstlisting}
    \end{tcolorbox}

    \noindent From the above implementations, it can be seen how important the \textit{tokenizer} is by parsing groups of characters like ``\textbf{String }",``\textbf{Integer }", and ``\textbf{ = }". Additionally, binding operators combine parsers and provide a smooth transition between each one of them. The \textbf{result} parser is utilized to yield a list of tuples containing the corresponding parsed AST and unparsed input string.

    \subsubsection{Input and Output}

    The behavior of input and output operations is represented with the keywords \textbf{get} and \textbf{print} respectively. The format in parsing input and output is the following: a keyword (either \textbf{get} or \textbf{print}), an opening bracket, variable name, and a closing bracket. The implementation of the parsers that will parse the input and output statements is presented below:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    parse_get :: Parse AST
    parse_get  = tokenize "get(" `bind` \get -> isword 
                                 `bind` \var -> singleChar ')' 
                                 `bind` \close -> result (Get var) 
     \end{lstlisting}
    \end{tcolorbox}

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    parse_print :: Parse AST
    parse_print  = tokenize "print(" `bind` \print -> isword 
                                     `bind` \var -> singleChar ')' 
                                     `bind` \close -> result (Print var) 
     \end{lstlisting}
    \end{tcolorbox}

    \noindent The construction of these parsers is much simpler that the parsers from variable declaration since there is not so much tokens to parse in this situation. The \textit{tokenizer} is again used to parse the keywords together with opening bracket: \textbf{"print("} and \textbf{get(}. The outcome in both parsers contains the \textbf{result} parser taking as input the AST values \textbf{Get var} or \textbf{Print var} (where \textit{var} is the string parsed by the \textit{isword} parser) and the remaining unparsed input string.

    \subsubsection{Variable Assignment}
    \subsubsection{While Loop}
